Predicting the Capture Rate of Pokemon

### 2022-11-22 Draft2.Rmd
progress

```{r}
# Loading all necessary packages
library(tidyverse)
library(dplyr)
library(tidymodels)
library(readr)
library(kknn)
# Assigning the data to a variable
pokemon <- read_csv("data/pokemon.csv")
tidymodels_prefer()
set.seed(0124)
```

@@

```{r}
# Selecting only the variables we want
pokemon <- pokemon %>% 
  select(c("abilities", "attack", "base_total", "capture_rate", "defense", "hp", "name", "sp_attack", "sp_defense", "speed", "type1", "generation", "is_legendary"))
head(pokemon)
```

@@

```{r}
# Creating recipe
pokemon_recipe <- recipe(capture_rate ~ attack + defense + hp + sp_attack + sp_defense + speed + type1 + generation + is_legendary + has_sturdy + has_swift_swim + has_keen_eye + has_chlorophyll + has_levitate, data = pokemon_train) %>%
  step_dummy(all_nominal_predictors()) %>% 
  step_center(all_predictors()) %>% 
  step_scale(all_predictors())
```

```{r}
# Creating folds
pokemon_folds <- vfold_cv(pokemon_train, v = 10)
```

@@

```{r}
# Fitting the models
lm_fit <- fit_resamples(lm_workflow, resamples = pokemon_folds)
```
```{r}
collect_metrics(lm_fit)
```

@@

### Ridge Regression   
```{r}
ridge_lasso_recipe <- recipe(capture_rate ~ attack + defense + hp + sp_attack + sp_defense + speed + type1 + generation + is_legendary + has_sturdy + has_swift_swim + has_keen_eye + has_chlorophyll + has_levitate, data = pokemon_train) %>%
  step_dummy(all_nominal_predictors()) %>% 
  step_novel(all_nominal_predictors()) %>% 
  step_zv(all_predictors()) %>% 
  step_normalize(all_predictors())

@@

```{r}
best_lasso_penalty <- select_best(tune_res2, metric = "rsq")
lasso_final <- finalize_workflow(lasso_workflow, best_lasso_penalty)
lasso_final_fit <- fit_resamples(lasso_final, resamples = pokemon_folds)
```

@@

```{r, message = FALSE, warning = FALSE}
poly_rec <- recipe(capture_rate ~ attack + defense + hp + sp_attack + sp_defense + speed + type1 + generation + is_legendary + has_sturdy + has_swift_swim + has_keen_eye + has_chlorophyll + has_levitate, data = pokemon_train) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_poly(all_numeric_predictors(), degree = tune())

@@

@@

@@

>>>>

```{r}
# Loading all necessary packages
library(tidyverse)
library(dplyr)
library(tidymodels)
library(readr)
library(kknn)
library(janitor)
# Assigning the data to a variable
pokemon <- read_csv("data/pokemon.csv")
tidymodels_prefer()
set.seed(0124)
```

@@

```{r}
# Selecting only the variables we want
pokemon <- pokemon %>% 
  select(c("abilities", "attack", "base_happiness",  "base_total", "capture_rate", "defense", "experience_growth", "height_m", "percentage_male", "hp", "name", "sp_attack", "sp_defense", "speed", "type1", "weight_kg", "generation", "is_legendary")) %>% 
  clean_names()
head(pokemon)
```

@@

```{r}
# Creating recipe
pokemon_recipe <- recipe(capture_rate ~ attack + defense + hp + sp_attack + sp_defense + speed + base_happiness + experience_growth + height_m + percentage_male + weight_kg + type1 + generation + is_legendary + has_sturdy + has_swift_swim + has_keen_eye + has_chlorophyll + has_levitate, data = pokemon_train) %>% 
  # imputing percentage male
  step_impute_linear(percentage_male, impute_with = imp_vars(attack, defense, sp_attack, sp_defense, speed, base_happiness, experience_growth, type1, generation, is_legendary, has_sturdy, has_swift_swim, has_keen_eye, has_chlorophyll, has_levitate)) %>% 
  # imputing height
  step_impute_linear(height_m, impute_with = imp_vars(attack, defense, sp_attack, sp_defense, speed, base_happiness, experience_growth, percentage_male, type1, generation, is_legendary, has_sturdy, has_swift_swim, has_keen_eye, has_chlorophyll, has_levitate)) %>% 
  # imputing weight
  step_impute_linear(weight_kg, impute_with = imp_vars(attack, defense, sp_attack, sp_defense, speed, base_happiness, experience_growth, height_m, percentage_male, type1, generation, is_legendary, has_sturdy, has_swift_swim, has_keen_eye, has_chlorophyll, has_levitate)) %>% 
  step_other(type1) %>% 
  # dummy coding nominal variables
  step_dummy(generation, is_legendary, type1, has_sturdy, has_swift_swim, has_keen_eye, has_chlorophyll, has_levitate) %>% 
  # normalizing
  step_center(all_predictors()) %>% 
  step_scale(all_predictors())
```

```{r}
# Creating folds
pokemon_folds <- vfold_cv(pokemon_train, v = 10, strata = capture_rate)
```

@@

```{r}
# Fitting the models
lm_fit <- fit_resamples(lm_workflow, resamples = pokemon_folds)
```

```{r}
collect_metrics(lm_fit)
```

@@

### Ridge Regression   
```{r}
ridge_lasso_recipe <- pokemon_recipe %>% 
  step_novel(all_nominal_predictors()) %>% 
  step_zv(all_predictors()) %>% 
  step_normalize(all_predictors())

@@

```{r}
best_lasso_penalty <- select_best(tune_res2, metric = "rmse")
lasso_final <- finalize_workflow(lasso_workflow, best_lasso_penalty)
lasso_final_fit <- fit_resamples(lasso_final, resamples = pokemon_folds)
```

@@

```{r, message = FALSE, warning = FALSE}
poly_rec <- pokemon_recipe %>% 
  step_poly(attack, defense, hp, sp_attack, sp_defense, speed, degree = tune())

ggplot(pokemon_train, aes(y = type1)) + geom_bar()

@@

```{r}
best_poly<- select_best(tune_res3, metric = "rmse")
poly_final <- finalize_workflow(poly_wf, best_poly)
poly_final_fit <- fit_resamples(poly_final, resamples = pokemon_folds)

collect_metrics(poly_final_fit)
```

@@

```{r}
autoplot(knn_tune)
```

@@

### Elastic Net

```{r, warning = FALSE, message = FALSE}
elastic_spec <- 
  linear_reg(penalty = tune(), mixture = tune()) %>% 
  set_mode("regression") %>% 
  set_engine("glmnet")

elastic_workflow <- workflow() %>% 
  add_recipe(pokemon_recipe) %>% 
  add_model(elastic_spec)

elastic_grid <- grid_regular(penalty(range = c(-5, 5)), mixture(range = c(0,1)), levels = 10)

elastic_tune <- tune_grid(
  elastic_workflow,
  resamples = pokemon_folds,
  grid = elastic_grid
)
```

```{r}
autoplot(elastic_tune)
```

```{r}
best_elastic <- select_best(elastic_tune, metric = "rmse")
elastic_final <- finalize_workflow(elastic_workflow, best_elastic)
elastic_final_fit <- fit_resamples(elastic_final, resamples = pokemon_folds)

collect_metrics(elastic_final_fit)
```
